Bias in the Estimation of the Value of VRA over URA: A Case of Mis-speficied Geographically Weighted Regression Models

### 2023-11-12 Writing/manuscript_gwr.rmd
modified manuscript

Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau in reality. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability. The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we have raised here is likely to be observed for other statistical methods as well because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods. In the future, it would be interesting to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.

>>>>

Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau. @trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR. The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically. Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink (critical input rate where yield plateau is reached). Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form. It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and may need to be incorporated into future research. Note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.

Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability. The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we have raised here is likely to be observed for other statistical methods as well because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.

<!-- # Conclusions

This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE. We showed that VRA based on GWR provides only small economic benefits over URA based on SCAM. The relative performances of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio. Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations. It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation. -->
